\documentclass[10pt]{article}

\title{Your Title Goes Here}
\author{As generated from LibraryThing\\With Ruby, ERB, and \LaTeX}
\date{} % Leave empty for no date, or fill in yourself

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{microtype} % Improve subtle kerning

\usepackage{lmodern} % Nice font

\usepackage{longtable} % Split tables across pages

\leftskip 0.25in
\parindent -0.25in

\begin{document}

\maketitle

\section*{Author Listing}

\begin{longtable}{p{0.66\textwidth} l}


{\MakeUppercase{\textsf{\textbf{\textbf{Davies, Robertson} and \textbf{Grant MacDonald} (Illustrator).}}}}\hspace{2em}Shakespeare for Young Players: A Junior Course
\newline
\textit{Toronto: Clarke, Irwin, 1942.}\newline
&

\MakeLowercase{\textsc{DRAM DAVIES}} \\


{\MakeUppercase{\textsf{\textbf{\textbf{Jenoff, Marvyne}.}}}}\hspace{2em}Crackerjack Umbrella
\newline
\textit{Toronto: Twoffish Press, 2008.}\newline\textsc{inscribed}\newline
&

\MakeLowercase{\textsc{POE JENOFF}} \\


------------\hspace{2em}Hercules by My Side
\newline
\textit{Toronto: Twoffish Press, 2006.}\newline
&

\MakeLowercase{\textsc{FIC JENOFF}} \\


{\MakeUppercase{\textsf{\textbf{\textbf{Latham, Sheila} (Editor) and \textbf{David Latham} (Editor).}}}}\hspace{2em}Magic Lies: The Art of W.O. Mitchell
\newline
\textit{Toronto: University of Toronto Press, 1997.}\newline
&

\MakeLowercase{\textsc{819 MIT LAT}} \\


{\MakeUppercase{\textsf{\textbf{\textbf{McBurney, Margaret} and \textbf{Ann Schabas} (Editor).}}}}\hspace{2em}The Great Adventure: 100 Years at the Arts \& Letters Club
\newline
\textit{Toronto: Arts \& Letters Club of Toronto, 2007.}\newline
&

\MakeLowercase{\textsc{706 ALC MCBU}} \\


{\MakeUppercase{\textsf{\textbf{\textbf{Skene-Melvin, David} and \textbf{Norbert Spehner} (Assistant).}}}}\hspace{2em}Canadian Crime Fiction: An Annotated Comprehensive Bibliography of Canadian Crime Fiction From 1817 to 1996, and Biographical Dictionary of Canadian Crime Writers, With an Introductory Essay on the History and Development of Canadian Crime Writing
\newline
\textit{Shelburne ON: Battered Silicon Dispatch Box, 1996.}\newline
&

\MakeLowercase{\textsc{016 SKE 1996}} \\


\end{longtable}

\newpage

\section*{Classified Listing}

\noindent



016 SKE 1996\newline
\MakeUppercase{\textsf{\textbf{\textbf{Skene-Melvin, David} and \textbf{Norbert Spehner} (Assistant).}}}\hspace{1em}\textsf{Canadian Crime Fiction: An Annotated Comprehensive Bibliography of Canadian Crime Fiction From 1817 to 1996, and Biographical Dictionary of Canadian Crime Writers, With an Introductory Essay on the History and Development of Canadian Crime Writing}
\newline
\textit{Shelburne ON: Battered Silicon Dispatch Box, 1996.}\newline


706 ALC MCBU\newline
\MakeUppercase{\textsf{\textbf{\textbf{McBurney, Margaret} and \textbf{Ann Schabas} (Editor).}}}\hspace{1em}\textsf{The Great Adventure: 100 Years at the Arts \& Letters Club}
\newline
\textit{Toronto: Arts \& Letters Club of Toronto, 2007.}\newline


819 MIT LAT\newline
\MakeUppercase{\textsf{\textbf{\textbf{Latham, Sheila} (Editor) and \textbf{David Latham} (Editor).}}}\hspace{1em}\textsf{Magic Lies: The Art of W.O. Mitchell}
\newline
\textit{Toronto: University of Toronto Press, 1997.}\newline


DRAM DAVIES\newline
\MakeUppercase{\textsf{\textbf{\textbf{Davies, Robertson} and \textbf{Grant MacDonald} (Illustrator).}}}\hspace{1em}\textsf{Shakespeare for Young Players: A Junior Course}
\newline
\textit{Toronto: Clarke, Irwin, 1942.}\newline


FIC JENOFF\newline
\MakeUppercase{\textsf{\textbf{\textbf{Jenoff, Marvyne}.}}}\hspace{1em}\textsf{Hercules by My Side}
\newline
\textit{Toronto: Twoffish Press, 2006.}\newline


POE JENOFF\newline
------------\hspace{1em}\textsf{Crackerjack Umbrella}
\newline
\textit{Toronto: Twoffish Press, 2008.}\newline\textsc{inscribed}\newline


\end{document}
